\subsection{Machine learning}

\acrfull{ml} is the branch of \acrshort{ai} that studies how to give machines the ability to learn, understanding it as the generalisation of knowledge from a set of experiences. This learning can be divided into \cite{amodernapproach}:
\begin{itemize}
\item Supervised: The algorithm learns on a labeled dataset, providing an answer key that the algorithm can use to evaluate its accuracy on training data \cite{nvidia}.
\item Unsupervised: Given the unlabeled data, the algorithm tries to capture meaning by extracting characteristics and patterns by itself \cite{nvidia}.
\item Reinforced: An algorithm is trained with a system of rewards, providing feedback when an artificial intelligence agent performs the best action in a particular situation \cite{nvidia}.
\end{itemize}


\acrlong{ml} is the main branch of \acrshort{ai}, since the other branches either imitate behaviour or learn from experience, i.e., they use \acrshort{ml} to perform the task at hand. It is one thing to program a machine so that it can move, but it is another thing for the machine to learn to move. Likewise, it is not the same to program which components form a face of a person as it is to automatically learn that it is a face. This paradigm shift is what differentiates the \acrshort{ml} from the \acrshort{ai}, and that is why it should not be thought that they are the same concepts.
\newline


\acrlong{ml} is the systematic study of algorithms and systems that improve your knowledge or experienced performance. In this subcategory there are different types of applications, some of them \cite{amodernapproach}:
\begin{itemize}
\item Regression models: These are models that predict the value of one or more variables given an input vector. A linear function is the simplest regression model, but the more complex regression models are formed by a fixed set of non-linear functions, known as base functions \cite{flach}. Algorithms such as the acrfull{svm} or the \acrfull{nn} are based on this type of model. The latter will be used in this paper.

\item Decision trees

\item Classification models
\item Grouping techniques
\end{itemize}

\input{sections/state-of-art/automated-learning-sections/models}